---
title: "Exploitation Rates WCVI Chinook"
author: "Carrie Holt"
date: "7/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = normalizePath(".."))  


library(tidyverse)
library(ggplot2)
```


Pre-terminal exploitation rates for Robertson Creek CWT Hatchery Indicator Stock were are provided by Diana Dobson in 2019 and updated by Diana McHugh in 2021. Age-specific exploitation rates were multiplied by the annual proportion of natural spawners at each age in that return year to derive an overall exploitation rate each year (shown below). 

```{r ERs, fig.cap = "**Figure 1**. Pre-terminal exploitation rates for Robertson Creek CWT indicators 1985-2019."}
# setwd('..')
# rootDir<-getwd()
# codeDir<-paste(rootDir,"/Code",sep="")
# wcviCKDir<-paste(rootDir,"/WCVIChinookStudy",sep="")

# ERs <- read.csv(paste(wcviCKDir, "/DataIn/ER.csv", sep="")
ERs <- read.csv("DataIn/ER.csv")
ggplot(ERs,aes(Year, ER)) + geom_point() + 
  # xlab("Année") +
  # ylab("Taux d’exploitation") +
  geom_line()

```



The mean exploitation rate over the entire time-series is `r round(mean(ERs$ER),2)`, and for the last 10 years is `r round(mean(ERs %>% filter(Year>=2010) %>% pull(ER)),2)`. The coefficient of variation (SD/mean) in exploitation rates for the entire time-series is `r round(sd(ERs$ER)/mean(ERs$ER),2)`, and for the last 10 years is `r round(sd(ERs %>% filter(Year>=2010) %>% pull(ER)) / mean(ERs %>% filter(Year>=2010) %>% pull(ER)),2)`. The recent cv in exploitation rates, `r round(sd(ERs %>% filter(Year>=2010) %>% pull(ER)) / mean(ERs %>% filter(Year>=2010) %>% pull(ER)),2)`,  is used to parameterize interannaual variability in exploitatoin rates in the forward projections (Fig. 2). Half of that value, `r round(sd(ERs %>% filter(Year>=2010) %>% pull(ER)) / mean(ERs %>% filter(Year>=2010) %>% pull(ER)),2)/2`, is used as to parameterize the variability among inlets (varied in sensitivity analyses from 0 to `r round(sd(ERs %>% filter(Year>=2010) %>% pull(ER)) / mean(ERs %>% filter(Year>=2010) %>% pull(ER)),2)`). The cv over the entire time-series is also shown (Fig. 2).

```{r pressure, echo=FALSE, fig.cap="**Figure 2.** Variability in simulated exploitation rates over time (cv=0.17) and among inlets (cv=0.085), from the average explotation of 0.30. An upper value for interannual variability is also shown (0.27)."}
nTrials <- 100000
canERlabel <- 0.30
set.seed(100)

# Density of ERs with cvER=0.085 ( among CUs)
canER <- canERlabel
cvER <- 0.085
sigCanER <- cvER*canER
shape1 <- canER^2 * (((1-canER)/sigCanER^2)-(1/canER))
shape2 <-shape1 * (1/canER-1)
out1 <- rbeta(nTrials,shape1,shape2)

# Density of ERs with cvER=0.17
cvER <- 0.17
sigCanER <- cvER*canER
shape1 <- canER^2 * (((1-canER)/sigCanER^2)-(1/canER))
shape2 <-shape1 * (1/canER-1)
out2 <- rbeta(nTrials,shape1,shape2)

# Density of ERs with cvER=0.17
cvER <- 0.27
sigCanER <- cvER*canER
shape1 <- canER^2 * (((1-canER)/sigCanER^2)-(1/canER))
shape2 <-shape1 * (1/canER-1)
out3 <- rbeta(nTrials,shape1,shape2)


out <- data.frame( cvER = c(rep("0.085",nTrials), rep("0.17",nTrials),
                            rep("0.27",nTrials)),
                   ExploitationRate = c(out1, out2, out3) )




g <- out %>% dplyr::filter(cvER=="0.085"|cvER=="0.17"|cvER=="0.27") %>%
  ggplot(aes(ExploitationRate, colour = cvER, fill = cvER)) +
  geom_density (alpha = 0.1) +
  xlim (0,1) +
  geom_vline (xintercept = canERlabel) +
  theme(axis.title.x = element_text(size=18),
        axis.title.y = element_text(size=18))
g

```


